Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-10-13 manuscript/Chapter2-manuscript.Rmd
updated fig 2 and 3 + MS

Because a maximum of four prey can be captured in the game, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion. The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link for all models. The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} \sim Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters. We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id_{0,i}$) followed a Gaussian distribution with estimated variance ($id_{0,i} \sim N(0, V_{id})$). We parametrized all models to run 4 MCMC chains with 1000 posterior samples. We ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models. The first 500 iterations were used as warmups. We provide a description on how we specified the priors for each model in the supporting information. After fitting the 3 models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017].

@@

We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical linear model (MDHLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].

@@

Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a general population trend with varying intercepts only (Table x.). Moreover, we did not detect a relationship between experience (i.e. the cumulative amount of matches played) and hunting success, such that players did not optimize their success with increasing experience as we expected (Figure 1 A). However, predators did differ in their average hunting success across the study period (Figure 1 B).

<br>

blablabla

@@

set_caption(
  tab1,
  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother",
  style = "Table Caption"
)

@@

```{r out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience. (A) Coefficient of variation for the among individual differences in average behavior. (B) Coefficient fo variation for the among individual differences in within individual variance (i.e. specialization)."}

@@

blablabla figure 3

```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}

@@

blablabla figure 4

```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}

>>>>

Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms" (for an overview, see https://paul-buerkner.github.io/brms/articles/brms_customfamilies.html). Thus, hunting success was estimated as the probability of capturing the four prey ($p_i$), drawn from a Beta distribution ($p_i \sim Beta(\mu_i, \phi) = Beta(\alpha = \mu\phi, \beta = (1 - \mu)\phi)$) with mean ($\mu \in [0,1]$) and shape ($\phi > 0$) parameters. We employed a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the shape parameter ($\phi$) was estimated with an identity link for all models.

We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id_{0,i}$) followed a Gaussian distribution with estimated variance ($id_{0,i} \sim N(0, V_{id})$). We parametrized all models to run 4 MCMC chains with 1000 posterior samples. We ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models. The first 500 iterations were used as warmups. We provide a description on how we specified the priors for each model in the supporting information. After fitting the 3 models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017].

@@

We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].

@@

Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a global smoother with varying intercepts only (Table S1 in the supporting information). The model detected only a weak relationship between hunting success and experience (i.e. the cumulative amount of matches played), such that players did not substantially optimize their success with increasing experience as we expected (Table 1 and Figure S1 in the supporting information). However, predators did differ in their average hunting success across the study period (Figure S1). *peut être coder un autre modèle où je contrôle pour les proies afin de voir si les différences de succès disparaissent*

@@

set_caption(
  tab1,
  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale",
  style = "Table Caption"
)

## Effect of experience on the development of behavioral specialization

```{r out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience. (A) Coefficient of variation for the among individual differences in average behavior. (B) Coefficient fo variation for the among individual differences in intra individual variance (i.e. specialization)."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))

@@

```{r out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioral variation (i.e. specialization) of predators when they were (A) novices and (B) advanced. The red band displays the 95% CI of the intercept for the intra individual variance in predator speed."}

@@

## Relationship between behavioral specialization and prey variability

```{r out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success. Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue). Larger dark blue circles indicate stronger positive correlations, while larger dark red circles indicate stronger negative correlations. The black squares indicate correlations between different experience levels."}

@@

## Hunting success of behavioral specialists vs generalists

*relationship between IIV of prey and success fades with experience*

```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novices. (C) and (D) Advanced."}
